---
title: "Multi-analysiss"
author: "Alberto pantoja"
site: bookdown::bookdown_site
apple-touch-sin: "icon_192.png"
apple-touch-icon-size: 192
favicon: "icon_32.png"
github-repo: "AlbertOmics/Brain_multi_study_analysis"
documentclass: book
output:
  bookdown::gitbook:
    css: "style.css"
    
---


<!-- README.md is generated fom README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Multi studio analysis
:)
<!-- badges: start -->
<!-- badges: end -->

The goal of Multi studio analysis is to merge multiple Ilumina 4000 data from mouse...

We merged the information of the following studios and based on their genetic signature, we assigned sex on the mouses that did not have it assigned:


SRA_list <- c('SRP215380',
'SRP128050',
'SRP199237',
'SRP152324',
'SRP152966',
'SRP131336',
'SRP130908',
'SRP100500',
'SRP125754',
'SRP174174',
'SRP099692'
)



```{r cars, echo=FALSE, message=FALSE}

library("edgeR") # BiocManager::install("edgeR", update = FALSE)
library("ggplot2")
library("limma")
library("EnhancedVolcano")
library("pheatmap")
library("RColorBrewer")

load("~/Miguel_Github/MERS_CoV_analysis/processed_data/df_female_genotype.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/df_male_genotype.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/df_WT_genotype.RData")

load("~/Miguel_Github/MERS_CoV_analysis/processed_data/exprs_heatmap_WT_genotype.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/exprs_heatmap_male_genotype.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/exprs_heatmap_female_genotype.RData")
```

# Model based on genotype

## WT - Genotype

```{r , echo = FALSE}

df_WT_genotype$Genotype <- factor(ifelse(!df_WT_genotype$Genotype %in% c('wild type','wt'), "Non-WT", "WT"))

df_WT_genotype$Age <- factor(ifelse(df_WT_genotype$Age == 'embryo', "embryo", ifelse(df_WT_genotype$Age == 'unknown', "unknown", "adult")))

  ## Hagamos un heatmap
  pheatmap(
    exprs_heatmap_WT_genotype,
    cluster_rows = TRUE,
    cluster_cols = TRUE,
    show_rownames = TRUE,
    show_colnames = FALSE,
    annotation_col = df_WT_genotype
  )

```

## Female - Genotype


```{r pressure, echo = FALSE}

df_female_genotype$Genotype <- factor(ifelse(!df_female_genotype$Genotype %in% c('wild type','wt'), "Non-WT", "WT"))

df_female_genotype$Age <- factor(ifelse(df_female_genotype$Age == 'embryo', "embryo", ifelse(df_female_genotype$Age == 'unknown', "unknown", "adult")))

  ## Hagamos un heatmap
  pheatmap(
    exprs_heatmap_female_genotype,
    cluster_rows = TRUE,
    cluster_cols = TRUE,
    show_rownames = TRUE,
    show_colnames = FALSE,
    annotation_col = df_female_genotype
  )

```

## Male - Genotype

```{r , echo = FALSE}

df_male_genotype$Genotype <- factor(ifelse(!df_male_genotype$Genotype %in% c('wild type','wt'), "Non-WT", "WT"))

df_male_genotype$Age <- factor(ifelse(df_male_genotype$Age == 'embryo', "embryo", ifelse(df_male_genotype$Age == 'unknown', "unknown", "adult")))



  ## Hagamos un heatmap
  pheatmap(
    exprs_heatmap_male_genotype,
    cluster_rows = TRUE,
    cluster_cols = TRUE,
    show_rownames = TRUE,
    show_colnames = FALSE,
    annotation_col = df_male_genotype
  )

```

```{r}
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/df_female_age.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/df_male_age.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/df_WT_age.RData")

load("~/Miguel_Github/MERS_CoV_analysis/processed_data/exprs_heatmap_WT_age.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/exprs_heatmap_male_age.RData")
load("~/Miguel_Github/MERS_CoV_analysis/processed_data/exprs_heatmap_female_age.RData")
```


# Model based on age

## WT - age

```{r , echo = FALSE}

df_WT_age$Genotype <- factor(ifelse(!df_WT_age$Genotype %in% c('wild type','wt'), "Non-WT", "WT"))

df_WT_age$Age <- factor(ifelse(df_WT_age$Age == 'embryo', "embryo", ifelse(df_WT_age$Age == 'unknown', "unknown", "adult")))

  ## Hagamos un heatmap
  pheatmap(
    exprs_heatmap_WT_age,
    cluster_rows = TRUE,
    cluster_cols = TRUE,
    show_rownames = TRUE,
    show_colnames = FALSE,
    annotation_col = df_WT_age
  )

```

## Female - age


```{r , echo = FALSE}

df_female_age$Genotype <- factor(ifelse(!df_female_age$Genotype %in% c('wild type','wt'), "Non-WT", "WT"))

df_female_age$Age <- factor(ifelse(df_female_age$Age == 'embryo', "embryo", ifelse(df_female_age$Age == 'unknown', "unknown", "adult")))

  ## Hagamos un heatmap
  pheatmap(
    exprs_heatmap_female_age,
    cluster_rows = TRUE,
    cluster_cols = TRUE,
    show_rownames = TRUE,
    show_colnames = FALSE,
    annotation_col = df_female_age
  )

```

## Male - age

```{r , echo = FALSE}

df_male_age$Genotype <- factor(ifelse(!df_male_age$Genotype %in% c('wild type','wt'), "Non-WT", "WT"))

df_male_age$Age <- factor(ifelse(df_male_age$Age == 'embryo', "embryo", ifelse(df_male_age$Age == 'unknown', "unknown", "adult")))



  ## Hagamos un heatmap
  pheatmap(
    exprs_heatmap_male_age,
    cluster_rows = TRUE,
    cluster_cols = TRUE,
    show_rownames = TRUE,
    show_colnames = FALSE,
    annotation_col = df_male_age
  )

```
